MSHS COVID-19 Vaccinations

### 2021-05-18 Mimic Historical Arrived and Scheduled Spreadsheet.Rmd
Start working on a script to mimic original daily arrived and scheduled visit analysis using historical repository.

# Determine whether or not to update an existing repo
update_repo <- TRUE

# Determine whether or not to update an existing repo
initial_run <- FALSE
update_repo <- TRUE

@@

# Store today's date
today <- Sys.Date()

@@

  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_AM_Repo/*.*"),
                 caption = "Select this morning's schedule repository"))

@@

# Import MSSN data from Tableau
mssn_admin <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select latest MSSN Tableau Administration Data"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

mssn_admin <- mssn_admin[1:nrow(mssn_admin) - 1, ]

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
```

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

@@

```{r Combine data across all sites}

# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

@@

```{r Create and combine tables with vaccine administration and schedule data}
# Create a template of all sites, vaccine dates, and doses ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

@@

site_dose_rep <- cbind(site_rep, dose_rep)

site_dose_rep <- site_dose_rep %>%
  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
  arrange(Site, Dose)

@@

site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
                                                site_this_week_prior_days_templ,
                                                by = c("Site" = "Site"))

@@

site_dose_next_7days_templ <- left_join(site_dose_rep,
                                        site_next_7days_templ,
                                        by = c("Site" = "Site"))

# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Summarize administered doses for prior weeks -----------------
prior_weeks_admin <- daily_sched_summary %>%
  filter(VaccWeek < this_week) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize total doses administered and scheduled this week through today -----
this_week_admin_to_date <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate <= today) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Combine with template to ensure holidays are included
this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
                                   this_week_daily_admin,
                                   by = c("Site" = "Site",
                                          "Dose" = "Dose",
                                          "ApptDate" = "ApptDate"))

>>>>

# Determine whether or not to update an existing repo
initial_run <- FALSE
update_repo <- FALSE

@@

# Store today's date
# today <- Sys.Date()
today <- as.Date("3/31/21", format = "%m/%d/%y")

@@

  sched_repo <- readRDS(
    choose.files(default = paste0(user_directory,
                                  "/R_Sched_PM_Huddle_Repo/*.*"),
                 caption = "Select the desired schedule repository"))

@@

# Import MSSN data from Tableau
mssn_employee <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select MSSN Tableau Administration Data for Employees"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

mssn_nonemployee <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select MSSN Tableau Administration Data for Non-Employees"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

mssn_employee <- mssn_employee[1:nrow(mssn_employee) - 1, ]
mssn_nonemployee <- mssn_nonemployee[1:nrow(mssn_nonemployee) - 1, ]

mssn_employee <- mssn_employee %>%
  mutate(`Pod Type` = "Employee")

mssn_nonemployee <- mssn_nonemployee %>%
  mutate(`Pod Type` = "Patient")

mssn_admin <- rbind(mssn_employee, mssn_nonemployee)

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses", "Pod Type")
```

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           `Pod Type`,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

@@

```{r Combine data across all sites}
# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

@@

```{r Create and combine tables with vaccine administration and schedule data}
# Create a template of all sites, vaccine dates, doses, and pod types ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

@@

site_dose_templ <- cbind(site_rep, dose_rep)

site_dose_templ <- site_dose_templ %>%
  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
  arrange(Site, Dose)

pod_rep <- data.frame("Pod Type" = rep(pod_type,
                                       length(all_sites)))

site_pod_rep <- data.frame("Site" = sort(rep(all_sites,
                                             length(pod_type))))

site_pod_templ <- cbind(site_pod_rep, pod_rep)

site_pod_templ <- site_pod_templ %>%
  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
  arrange(Site, Pod.Type)

site_dose_pod_templ <- left_join(site_dose_templ, site_pod_templ,
                                 by = c("Site" = "Site"))

@@

site_dose_this_week_prior_days_templ <- left_join(site_dose_pod_templ,
                                                  site_this_week_prior_days_templ,
                                                  by = c("Site" = "Site"))

@@

site_dose_next_7days_templ <- left_join(site_dose_pod_templ,
                                        site_next_7days_templ,
                                        by = c("Site" = "Site"))

# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, `Pod Type`, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

admin_to_date2 <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, `Pod Type`, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Summarize administered doses for prior weeks -----------------
prior_weeks_admin <- daily_sched_summary %>%
  filter(VaccWeek < this_week) %>%
  group_by(Site, `Pod Type`, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize total doses administered and scheduled this week through today -----
this_week_admin_to_date <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate <= today) %>%
  group_by(Site, `Pod Type`, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, `Pod Type`, Dose, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Combine with template to ensure holidays are included
this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
                                   this_week_daily_admin,
                                   by = c("Site" = "Site",
                                          "Pod.Type" = "Pod Type",
                                          "Dose" = "Dose",
                                          "ApptDate" = "ApptDate"))
